---
title: "Shiny app for computing and evaluating the alpha and beta parameters of Beta distributions"
output: 
  github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Package installation and update

The easiest way to install the `betadistapp` package is from Github. This requires installing the `devtool` package first.

```{r, eval = FALSE, message=FALSE}
install.packages("devtools")
```

Then load the `devtool` package:

```{r, eval = FALSE}
library(devtools)
```

In order to install (or update) the STOCfree package, run the following line:

```{r, eval = FALSE}
install_github("AurMad/betadistapp")
```

## The `shiny_beta()` function

The package contains a single function called `shiny_beta()`. This function launches a shiny app. The user can specifiy either the mean and standard deviations of a Beta distributions using sliding bars. The corresponding Beta distributions will be plotted and the corresponding alpha and beta parameters will be displayed. The used can also enter the alpha and beta paramters which will lead to the corresponding distribution being displayed.

```{r, eval = FALSE}
library(betadistapp)

shiny_beta()
```


